%-------------------------
% Resume in Latex
% Authors : Chris Bloodsworth, Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Christopher Bloodsworth} \\ \vspace{1pt}
    \small 941-445-3628 $|$ \href{christopherbloodsworth@gmail.com}{\underline{christopherbloodsworth@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/chris-bloodsworth/}{\underline{linkedin.com/in/chris-bloodsworth}} $|$
    \href{https://github.com/cbloodsworth}{\underline{github.com/cbloodsworth}} \\
    \small {Personal Website:} \href{https://cbloodsworth.github.io}{\underline{https://cbloodsworth.github.io}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Florida}{Gainesville, FL}
      {Bachelor of Science in Computer Science}{January 2019 -- May 2024}
      \resumeItemListStart
        \resumeItem{Majoring in Computer Science and Engineering with a minor in Mathematics. GPA: 3.73}
        \resumeItem{Member of the engineering honor society Tau Beta Pi.}
      \resumeItemListEnd  
    \resumeSubheading
      {State College of Florida}{Sarasota, FL}
      {Associate's in Liberal Arts and Sciences}{August 2018 -- December 2020}
      \resumeItemListStart
        \resumeItem{Member of Gator Engineering @ SCF, taking both UF and SCF courses before transferring to UF proper.}
        \resumeItem{Graduated Magna Cum Laude and as the designated recipient of “Outstanding Student in Mathematics.”}
      \resumeItemListEnd  
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Software Engineering Intern}{May 2023 -- Present}
      {MRSL Real-Time Systems Laboratory}{Sarasota, FL}
      \resumeItemListStart
        \resumeItem{Working tightly with performance-critical digital signal processing (DSP) applications in C++.}
        \resumeItem{Designing a parallelized DSP algorithm to operate synchronously across pods in a Kubernetes cluster.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Technical Lead}{September 2022 -- Current}
      {Open-Source Club}{University of Florida}
      \resumeItemListStart
        \resumeItem{Manages twice-weekly discussions and working sessions for various open-source projects.}
        \resumeItem{In Spring 2023, led OSC-API, a subgroup of Open-Source Club dedicated to the development of small-scale APIs.}
        \resumeItem{In Fall 2022, led the development for AL-Bot 2.0, a discord bot written in Typescript using the Discord.js API.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Manuela}{March 2023}
      {RoboTech 2023}{Georgia Institute of Technology}
      \resumeItemListStart
        \resumeItem{AI chat buddy written in Python. Uses OpenAI’s DaVinci GPT-3 model, Google Text-to-Speech and OpenCV’s face detection API to detect the user’s current mood and provide meaningful, human conversation.}
        \resumeItem{In a four-person hackathon group, programmed the mood-detection portion and the main driver.}
    \resumeItemListEnd

    \resumeSubheading
      {Swamp Investigator}{January 2023}
      {SwampHacks IX}{University of Florida}
      \resumeItemListStart
        \resumeItem{Procedurally generated exploration game made in Python using the PyGame framework.}
        \resumeItem{Developed world generation using Perlin noise algorithms to create a realistic swamp to explore.}
      \resumeItemListEnd

    \resumeSubheading
      {File Systems}{December 2022}
      {COP4600: Operating Systems}{University of Florida}
      \resumeItemListStart
        \resumeItem{Using C++ in a virtual Ubuntu environment, created a program that could read and display the contents of WAD files. Integrated this with the FUSE API (filesystem in userspace) to create a fully navigable file system.}
      \resumeItemListEnd

    \resumeSubheading
      {PLC Language Compiler}{April 2023}
      {COP4020: Programming Language Concepts}{University of Florida}
      \resumeItemListStart
        \resumeItem{Designed and implemented a compiler for a made-up language to Java code.}
        \resumeItem{Included parsing, AST generation and type-checking.}
        \resumeItem{Written in Java and makes use of a number of popular object-oriented design patterns such as the Visitor and the Abstract Factory.}
      \resumeItemListEnd

    \resumeSubheading
      {"ProtestPlots" Scrum Master \& Python Developer}{September 2022}
      {CEN3031: Intro to Software Engineering}{University of Florida}
      \resumeItemListStart
        \resumeItem{Developed a Python script using Selenium and BeautifulSoup to gather and store data necessary to the web-app.}
        \resumeItem{Held stand-ups multiple times a week to discuss and resolve impediments that the team may face, estimated effort-hours of tasks, and facilitated sprints with Jira.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd



%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C++, Java, Python, C, JavaScript (TypeScript)} \\
     \textbf{Developer Tools}{: Linux, Bash, AWS (S3, EKS, SC2, Lambda), Git, Vim, SonarCloud, Docker, Kubernetes} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
